Circular Distributional Trees and Forests with an Application to Wind Direction Forecasting

### 2019-11-19 pkg/circtree/inst/wind_paper/draft/draft.Rnw
added linear illustration of fitted von Mises distribution to the circular illustration
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2885 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 1c302863dcc272c1b1ac574541263e64aa11f764

\begin{figure}[t]
\centering
\includegraphics[width=4cm]{density_vM.pdf}
\caption{Illustration of a distributional model fitted to circular data by maximum likelihood-estimation
employing the von Mises distribution. Empirical histogram (gray) and fitted density (red line) are depicted
along with the estimated location parameter (red hand).
}
\label{fig:density_vM} 
\end{figure}
\fixme{update figure 2d to 3d, using data of example tree}

Figure~\ref{fig:density_vM} illustrates a distributional model fitted to circular data
employing the von Mises distribution.
% on observed wind direction data from the airport of Innsbruck.
This example shows that reasonably well fitting probabilistic models can
be established for circular data by specifying an appropriate distribution family 
such as the von Mises distribution and estimating its parameters via maximum likelihood. 
However, this procedure considers only the response variable $Y$. Including covariates 
can improve any model remarkably as they might provide valuable additional information.
Therefore, distributional regression models are of high interest for all types of data,
including circular data.

>>>>

\begin{figure}[t]
%\centering
\hspace{-1cm}
\begin{minipage}{.5\textwidth}
  %\centering
  \includegraphics[width=1.2\linewidth]{density_linear.pdf}
  \end{minipage}%
\begin{minipage}{.5\textwidth}
  %\centering
  \includegraphics[width=1.2\linewidth]{density_circular.pdf}
\end{minipage}
\caption{Illustration of a distributional model fitted to circular data by 
  maximum likelihood-estimation employing the von Mises distribution. 
  Left panel: linear illustration. Right panel: circular illustration.
  In both panels the empirical histogram (gray) and fitted density (red line) are depicted along 
  with the estimated location parameter (red hand).
  }
  \label{fig:densities} 
  %\includegraphics[width=4cm]{density_vM.pdf}
\end{figure}
\fixme{update figure 2d to 3d, using data of example tree}

Figure~\ref{fig:densities} illustrates a distributional model fitted to circular data
employing the von Mises distribution.
% on observed wind direction data from the airport of Innsbruck.
This example shows that reasonably well fitting probabilistic models can
be established for circular data by specifying an appropriate distribution family 
such as the von Mises distribution and estimating its parameters via maximum likelihood. 
However, this procedure considers only the response variable $Y$. Including covariates 
can improve any model remarkably as they might provide valuable additional information.
Therefore, distributional regression models are of high interest for all types of data,
including circular data.
